\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-09-25 draft.tex
revise rest of sec:pref

\newcommand{\ve}{\theta}
\newcommand{\ta}{\theta}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\bte}{\bm{\tau^E}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

@@

Figure~\ref{fig:ext} illustrates the timing of the game. Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of anti-dumping duties $\bta = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the anti-dumping duties by choice of lobbying effort $e$.

@@

Assumption~\ref{as:ga_c} formalizes the intuition that the government agency favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity. It rules out higher effort making lower weights more likely and that the structure of uncertainty changes with increasing effort so that higher weights become more likely at an accelerating pace. Assumption~\ref{as:ga_ta} simply provides for an intuitive labeling so that larger realizations of $\ta$ increase the value of the political economy weight.

\textbf{LOBBY'S OBJECTIVE IS DIFFERENT HERE}

Given its expectations and the government agency's preferences, the home lobby chooses its lobbying effort ($e_b$ to influence the break decision and $e_n$ to influence the trade war tariff) to maximize the welfare function:
\begin{equation}
  \expect \left[U_L \right] = \Pr\left[ \text{TradeWar} \right] \left[ \pi(\tau^{\mathit{n}}) - e_n \right] + \Pr\left[ \text{TradeAgreement} \right] \pi(\tau^a) - e_b
  \label{eq:lv}
\end{equation}
where $\pi(\cdot)$ is the current-period profit and the subscript $X$ has been dropped for notational convenience.

@@

Finally, I assume that an external authority can ensure enforcement of the agreement.\footnote{Buzard (2015) considers a similar model in a repeated-game context and can therefore remove this restriction.}

>>>>

\newcommand{\ve}{\theta}
\newcommand{\ta}{\theta}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btad}{\bm{\tau^{ad}}}
\newcommand{\bte}{\bm{\tau^E}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

@@

Figure~\ref{fig:ext} illustrates the timing of the game. Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of anti-dumping duties $\btad = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the anti-dumping duties by choice of lobbying effort $e$.

@@

Assumption~\ref{as:ga_c} means that the government agency favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity. It rules out higher effort making lower weights more likely and that the structure of uncertainty changes with increasing effort so that higher weights become more likely at an accelerating pace. Assumption~\ref{as:ga_ta} simply provides for an intuitive labeling so that larger realizations of $\ta$ increase the value of the political economy weight.

Given its expectations and the government agency's preferences, the home lobby chooses its lobbying effort $e$ to maximize the welfare function:
\begin{equation}
  \expect \left[U_L \right] = \Pr\left[ \text{AD Renewal} \right]  \pi_X(\tau^{\mathit{ad}}) +\left\{1-\Pr\left[ \text{AD Renewal}\right]\right\} \ \pi_X(\tau^a) - e
  \label{eq:lv}
\end{equation}
where $\pi(\cdot)$ is the current-period profit.

@@

Finally, I assume that an external authority can ensure enforcement of the agreement.
